\LARGE \bf Detection of design pattern : A systematic mapping study

### 2015-12-31 article/main.tex
modified:   article/main.tex
modified:   main.tex
Data table

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{graphicx} % for png files
\graphicspath{{img/}}
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

@@

Design partterns are best pratice to recurring problems proposed by the Gang
of Four in their seminal book.

(Some study author) have been able to show that the presence of design patterns
can help one better understand a piece of software.

@@

However, no studies have been conducted to analyse the trends of the field.

@@

% Problem with that sentence
After having queried the database, we exported the results found and process to
screening.

@@

\begin{center}
  \begin{tabular}{ lcc }
    \bf Group & \bf \# of articles & \bf Cohen's kappa \\
    1 & ??? & 0.88 \\
    2 & ??? & 0.66 \\
    3 & ??? & 0.91 \\
  \end{tabular}
\end{center}

@@

\begin{itemize}
  \item Detection strategy:
    This determine the means on which the detection is based.
    Possible values: Artificial intelligence, Logic/Formalisation, Graph,
    Metric, Automata, Instrumentation/profiling and Others.

  \item Language dependance
    This category aims to classify detection methods on wether it is dependant
    on the language or not. 
    Possible values: Dependant or Independant
% This  specifies if the detection is langage dependent or independent,

  \item Analysis type
    This determine if a detection techniques use a static, dynamic or hybrid
    approach.
    Possible values: Static, Dynamic and Hybrid.

  \item Validation method:
    This specifies the type of scientific validation methods the article's 
    authors used for a detection method.
    Possible values: Benchmark, Case study, Experiment, Survey, Other and
    None.

  \item{Detection Level}
    This define on which level the detection method work : execution, source
    and model.
    It could be more than one level for a single method of detection.
    Possible values: Execution, Source and Model.

  \item Detected pattern types :
    This characterizes the type of design pattern a specific detection method
    can manage.
    The possible values for this category are Creationnal, Behavioural,
    Structural and Not specified.

  \item Pattern detection generality :
    This determine if a method is made to detect a single pattern or more than
    one pattern.
    Possible values: Specific, General.
\end{itemize}

@@

\subsubsection{Year distribution}
% Need to change the title for this graphic

@@

\subsubsection{Venue Distribution}
% Need a graphic for article by publishers.

\subsubsection{Detection Strategy}

\begin{center}
\includegraphics[scale=0.75]{detection_strategy.png}
\end{center}

\subsubsection{Analysis Type}

@@

\begin{center}
\includegraphics[scale=0.75]{analysis_type.png}
\end{center}

\subsubsection{Detected Pattern Types}

@@

\begin{center}
  \includegraphics[scale=0.65]{pattern_types.png}
\end{center}

This can be explained either by the fact that structural design patterns
detection is considered as an easy problem, thus less likely to be the main
focus of a research papers or by the possibility is that behavioural design
patterns are in fact easier to detect than structural ones.
However, we believe the first possibilty to be more likely.

\subsubsection{Language dependance}

\begin{center}
\includegraphics[scale=0.75]{language_generality.png}
\end{center}

\subsubsection{Detection Level}

\begin{center}
\includegraphics[scale=0.75]{detection_level.png}
\end{center}

\subsubsection{Detection generality}

\begin{center}
\includegraphics[scale=0.75]{detection_generality.png}
\end{center}

\subsubsection{Validation Methods}

\begin{center}
\includegraphics[scale=0.75]{validation_method.png}
\end{center}

\subsubsection{Detected pattern types according to analysis type}
% Need graphics

\section{SELECTION PROCESS RESULT}

>>>>

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{graphicx} % for png files
\graphicspath{{img/}}
\usepackage{multirow}
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

@@

Design partterns are best pratices proposed by the Gang of Four in their seminal
book to recurring design problems.

(Some study author) have been able to show that the presence of design patterns,
if correctly presented, can help one better understand a piece of software
[citation needed].
It is therefore desirable to be able to automatically extract those design
and present them in a digestible format.

@@

However, design pattern detection tools are still not featured in the typical
programmer toolbox.

No studies have been conducted to analyse the trends of the field.

This paper presents a systematic mapping study on design pattern detection
methods.
It is organized as follows: 
 The first section explains the systematic mapping process
 The second section analyses

@@

% Problem with that sentence: "and process"?  Maybe "proceeded" 
After having queried the database, we exported the results found and process to
screening.

@@

\begin{center}
  \begin{tabular}{ lcc }
    \bf Group & \bf \# of articles & \bf Cohen's kappa \\
    \hline {}
    1 & ??? & 0.88 \\
    2 & ??? & 0.66 \\
    3 & ??? & 0.91 \\
  \end{tabular}
\end{center}

@@

\begin{itemize}
  \item \textbf{Detection strategy}:
    This determine the means on which the detection is based.
    Possible values: Artificial intelligence, Logic/Formalisation, Graph,
    Metric, Automata, Instrumentation/profiling and Others.

  \item \textbf{Language dependance}:
    This category aims to classify detection methods on wether it is dependant
    on the language or not. 
    Possible values: Dependant or Independant
% This  specifies if the detection is langage dependent or independent,

  \item \textbf{Analysis type}:
    This determine if a detection techniques use a static, dynamic or hybrid
    approach.
    Possible values: Static, Dynamic and Hybrid.

  \item \textbf{Validation method}:
    This specifies the type of scientific validation methods the article's 
    authors used for a detection method.
    Possible values: Benchmark, Case study, Experiment, Survey, Other and
    None.

  \item \textbf{Detection Level}
    This define on which level the detection method work : execution, source
    and model.
    It could be more than one level for a single method of detection.
    Possible values: Execution, Source and Model.

  \item \textbf{Detected pattern types}:
    This characterizes the type of design pattern a specific detection method
    can manage.
    The possible values for this category are Creationnal, Behavioural,
    Structural and Not specified.

  \item \textbf{Pattern detection generality}:
    This determine if a method is made to detect a single pattern or more than
    one pattern.
    Possible values: Specific, General.
\end{itemize}

@@

\section{SELECTION PROCESS RESULTS}

\section{STUDY RESULTS}

\begin{center}
  \begin{tabular}{ lll }
    \bf Category & \bf Class & \bf \# of articles \\
    \hline
    \multirow{7}{*}{Detection Srategy}
    & \multicolumn{1}{l}{AI}           & \multicolumn{1}{l}{11} \\
    & \multicolumn{1}{l}{Logic}        & \multicolumn{1}{l}{22} \\
    & \multicolumn{1}{l}{Graph}        & \multicolumn{1}{l}{15} \\
    & \multicolumn{1}{l}{Metric}       & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Automata}     & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{Instr./Prof.} & \multicolumn{1}{l}{10} \\
    & \multicolumn{1}{l}{Pattern Mathching}
                                       & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Others}       & \multicolumn{1}{l}{23} \\
    \hline
    \multirow{2}{*}{\textbf{Language Dependance}}
    & \multicolumn{1}{l}{Dependant}    & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Independant}  & \multicolumn{1}{l}{XXX} \\
    \hline
    \multirow{3}{*}{\textbf{Analysis Type}}
    & \multicolumn{1}{l}{Static}       & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Dynamic}      & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{Hybrid}       & \multicolumn{1}{l}{XXX} \\
    \hline
    multirow{3}{*}{Detection Level}
    & \multicolumn{1}{l}{Execution}    & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Source}       & \multicolumn{1}{l}{44} \\
    & \multicolumn{1}{l}{Model}        & \multicolumn{1}{l}{7} \\
    \hline
    \multirow{2}{*}{Pattern detection generality}
    & \multicolumn{1}{l}{Specific}     & \multicolumn{1}{l}{XXX} \\
    & \multicolumn{1}{l}{General}      & \multicolumn{1}{l}{XXX} \\
    \hline
    \multirow{4}{*}{Detected Pattern Types}
    & \multicolumn{1}{l}{Creationnal}  & \multicolumn{1}{l}{23} \\
    & \multicolumn{1}{l}{Structural}   & \multicolumn{1}{l}{34} \\
    & \multicolumn{1}{l}{Behaviour}    & \multicolumn{1}{l}{49} \\
    & \multicolumn{1}{l}{Other/Not Specified}
                                       & \multicolumn{1}{l}{17} \\
    \hline
    \multirow{6}{*}{Validation Method}
    & \multicolumn{1}{l}{Benchmark}    & \multicolumn{1}{l}{7} \\
    & \multicolumn{1}{l}{Case Study}   & \multicolumn{1}{l}{40} \\
    & \multicolumn{1}{l}{Experiment}   & \multicolumn{1}{l}{8} \\
    & \multicolumn{1}{l}{Survey}       & \multicolumn{1}{l}{0} \\
    & \multicolumn{1}{l}{Other}        & \multicolumn{1}{l}{1} \\
    & \multicolumn{1}{l}{None}         & \multicolumn{1}{l}{11}
  \end{tabular}
\end{center}

\subsection{Yearly distribution}
% Need to change the title for this graphic

The yearly distribution gives us an interesting picture of the field.
Interest in design patterns detection technique started in the early
2000 and that interest is fading away since 2010.

This could indicate either that the field is mature and that research avenues
have been exhaused, that the field currently hit a roadblock, or that interest
is fading due to a lack of interest in the need for design pattern detection
tools.

@@

\subsection{Publication Venue Distribution}
% Need a graphic for article by publishers.

\subsection{Detection Strategy}

Most of the detection strategies used fall either in the 
\textit{logic/formalisation} or \textit{other} class.
The first one was probably overly broad since it included any solution using
inference rules engines, formalisation and semantic web ontologies.
Surprisingly, the latter strategy was the focus of many articles.

%\begin{center}
%\includegraphics[scale=0.75]{detection_strategy.png}
%\end{center}

\subsection{Analysis Type}

@@

%\begin{center}
%\includegraphics[scale=0.75]{analysis_type.png}
%\end{center}

\subsection{Detected Pattern Types}

@@

%\begin{center}
%  \includegraphics[scale=0.65]{pattern_types.png}
%\end{center}

This can be explained either by the fact that structural design patterns
detection is considered as an easy problem, thus less likely to be the main
focus of a research paper or by the possibility is that behavioural design
patterns are in fact easier to detect than structural ones.
However, we believe the first possibilty to be more likely.

\subsection{Language dependance}

%\begin{center}
%\includegraphics[scale=0.75]{language_generality.png}
%\end{center}

\subsection{Detection Level}

%\begin{center}
%\includegraphics[scale=0.75]{detection_level.png}
%\end{center}

\subsection{Detection generality}

This category was used to expose specific pattern detection methods.
Most papers present a general way to detect design patterns.

%\begin{center}
%\includegraphics[scale=0.75]{detection_generality.png}
%\end{center}

\subsection{Validation Methods}

%\begin{center}
%\includegraphics[scale=0.75]{validation_method.png}
%\end{center}

\subsection{Detected pattern types according to analysis type}
% Need graphics
